Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added new figure, more explanation to report
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@106 36274a68-8941-4c93-80ef-affaed5139da

\documentclass{article}
\newcommand{\oneFig}{.5}
\newcommand{\twoFig}{.42}
\newcommand{\fourFig}{.42}

@@

\begin{figure}
\centering
\includegraphics[scale=\oneFig]{figs/Solution3232nomesh.png}
\caption{Computed convection-diffusion solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-4)$.}
\end{figure}

@@

\subsection{$hp$-meshes}
\subsection{Parallel solvers}
\subsubsection{MUMPS}
\subsubsection{Conjugate gradients/static condensation}

@@

Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom. Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield 
\[
\left(\begin{array}{cc}
A &B\\
B^T &C
\end{array}
\right)
\left(\begin{array}{c}
u\\
f
\end{array}
\right) = 
\left(\begin{array}{c}
F\\
G
\end{array}
\right)
\]
where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
\[
(C-B^TA^{-1}B)f = G-B^TA^{-1}F
\]
Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.

>>>>

\documentclass{article}
\newcommand{\oneFig}{.45}
\newcommand{\twoFig}{.42}
\newcommand{\fourFig}{.42}

@@

\begin{figure}
\centering
\includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
\caption{Computed solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-5)$.}
\end{figure}

@@

\subsection{$hp$-meshes}
\subsection{Parallel solvers}
\subsubsection{MUMPS}

\subsubsection{Conjugate gradients/static condensation}

@@

Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom. Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield 
\[
\left(\begin{array}{cc}
A &B\\
B^T &C
\end{array}
\right)
\left(\begin{array}{c}
u\\
f
\end{array}
\right) = 
\left(\begin{array}{c}
F\\
G
\end{array}
\right)
\]
where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
\[
(C-B^TA^{-1}B)f = G-B^TA^{-1}F
\]
Since $A$ is easy to invert, and $B$ is a much smaller system, this static condensation would reduce the cost of the solve.
